---
title: "Alcohol vs Seat choice"
author: "Sandra Iovino"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

# Introduction  
The data came from UCDavis.csv in the year. 
our goal is to answer this question if there a difference between the alcohol consumed between row number you choose to sit in?   

## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.  

$H_A$: There is a difference in the average number drinks is different between at least two rows.

# Methods  
In the data set davisdata seat is a categorical variable, alcohol is numerical   

We try to predict alcohol ~ Seat so we use the  helper file    
Num ~ Cat  

# Results 

## Descriptive Results


### Graphical summary 

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

Now add in boxplot

```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))

basicCN + geom_boxplot()
```

  What this graph shows is that the back seat has the highest alcohol consume then the front or middle seats.  


### Numerical Summary
```{r}
favstats(alcohol~Seat,data=davisdata)
```
  When entering the Numerical Summary, this show that back seat consumes about 55% of alcohol, Front   consumes about 20% of alcohol and the middle is about 35% of alcohol. This means that the back seats    consumes more alcohol than the front or middle seats.    

### Inferential Results
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

 The P-value is 0.0001 which is less than 0.05 so we reject the null hypothesis. 
 
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

  This graph shows that there are more students sitting in the back who drink alcohol than the front and middle row. 

## Conclusions
 our goal is to answer this question if there a difference between the alcohol consumed between row number you choose to sit in? When doing our GGplots we noticed that more seaters in the back consumed more alcohol Our P-value was 0.0001 which is less than 0.05 so we reject the null hypothesis. There is a difference when seating in the back. More seater in the bak drink more alcohol than the ones in the middle or front.    


