---
title: "Alcohol vs Seat choice"
author: "Sandra Iovino"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

# Introduction  
The data came from UCDavis.csv in the year. 
our goal is to answer this question if there a difference between the alcohol consumed between row number you choose to sit in?   

## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.  

$H_A$: There is a difference in the average number drinks is different between at least two rows.

# Methods  
In the data set davisdata seat is a categorical variable, alcohol is numerical   

We try to predict alcohol ~ Seat so we use the  helper file    
Num ~ Cat  

# Results 

## Descriptive Results


### Graphical summary 

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

Now add in boxplot

```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))

basicCN + geom_boxplot()
```

  What this graph shows is that the back seat has the highest alcohol consume then the front or middle seats.  


### Numerical Summary


### Inferential Results

# Discussion and Conclusion




## Now with ggplot - first select the basic data


```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


## Conclusions


